### 2014-10-20 PAPER_AMMLY.tex
Theory fixed

Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. Furthermore let $\mathcal{A}_{\Lambda}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter). Note that the size of $\mathcal{A}_{\Lambda}$ is therefore $\Lambda^H$. Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$. Note that in general there exist elements in $\mathcal{A}_{\Lambda}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$). Thus Equation~\ref{eq:befrein} can be equivalently written as 
\[Y = q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!r_{i_1,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}A_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k},
\]
where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2 = \Psi$. Assuming the independence of $X$'s and $A's$ we get
\begin{equation}
Y_{\Lambda} := \mathbb{E}_A[Y] = q\!\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!r_{i_1,\dots,i_H}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k}.
\label{eq:befapprox}
\end{equation}
In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section). For our theoretical analysis we assume that $X$'s are independent identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$. This assumption is simplistic, yet pervasively used in machine learning theory (plethora of decoupling strategies are discussed in~\cite{opac-b1095246}).

@@

Finally we assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$. We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption). This assumption is in general consistent with the approach in~\cite{NIPS2013_5025} and allows us to treat $r$'s as probabilities rather than binary values. To be more specific, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ there exists $\delta \in [0,1]$ such that the following holds
\begin{equation}
(1-\delta)\sqrt{\frac{\Psi}{\Lambda^H}} \leq r_{i_1,i_2,\dots,i_H} \leq (1+\delta)\sqrt{\frac{\Psi}{\Lambda^H}},
\label{eq:uniform}
\end{equation}
where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $r_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{\Lambda^H}}$. Note that this condition can be sattified with small $\delta$ (close to $0$) if $s$ is sufficiently small.

Consider therefore an expression as follows
\begin{equation}
\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}X_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
\label{eq:approx}
\end{equation}
which can be thought of as an output of some network $\mathcal{M}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ among the total of $\Lambda$ weights, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely. Then the following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{\Lambda}$.

\begin{theorem}
Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \frac{1-\delta}{1+\delta}.
\]
\label{thm:unif}
\end{theorem}

We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}. Intuitively, for large-size networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently small (close to $0$) $\delta$ and preserve good accuracy (small $\epsilon$). \textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting. Besides then the data is mapped to a higher dimensional space.} Next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.

@@

\section{Proof of Theorem~\ref{thm:redun}}
\begin{proof}
Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2
\]
and
\[std(\hat{Y}_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
\]
\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
\]
Therefore
\begin{eqnarray*}
&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_{\Lambda})\\ 
&\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\! \frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}r_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!r_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
&\!\!\!\!\!\!\!\!\geq& \frac{1-\delta}{1+\delta}, 
\end{eqnarray*}
where the last inequality is the direct consequence of the uniformity assumption of Equation~\ref{eq:uniform}.
\end{proof}

>>>>

Let $\mathcal{W} = \{w_1,w_2,\dots,w_{\Lambda}\}$ be the set of all weights of the network. Furthermore let $\mathcal{A}$ denote the set of all $H$-length configuration of weights chosen from $\mathcal{W}$ (order of weights in a configuration does matter). Note that the size of $\mathcal{A}$ is therefore $\Lambda^H$. Also let $\mathcal{B}$ be a set such that each element correspond to the single configuration of weights from Equation~\ref{eq:befrein}, thus $\mathcal{B} = \{(w_{1,1}^1,w_{1,1}^2,\dots,w_{1,1}^H),(w_{1,2}^1,w_{1,2}^2,\dots,w_{1,2}^H),\dots,\\(w_{n_0,\gamma}^1,w_{n_0,\gamma}^2,\dots,w_{n_0,\gamma}^H)\}$, where every single weight comes from set $\mathcal{W}$. Note that in general there exist elements in $\mathcal{A}$ that will never appear in $\mathcal{B}$ (unless we allow repetition of weights in $\mathcal{W}$). Thus Equation~\ref{eq:befrein} can be equivalently written as 
\[Y = q\!\!\!\!\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\!\!\!r_{i_1,i_2,\dots,i_H}X_{i_1,i_2,\dots,i_H}A_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k},
\]
where $r_{i_1,i_2,\dots,i_H}$ denotes whether the configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ appeared in Equation~\ref{eq:befrein} or not thus $r_{i_1,i_2,\dots,i_H} \in \{0\cup{1}\}$ and furthermore $\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}r_{i_1,i_2,\dots,i_H} = \Psi$. Assuming the independence of $X$'s and $A's$ we get
\begin{equation}
Y_{\Lambda} := \mathbb{E}_A[Y] = q\!\!\!\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!r_{i_1,\dots,i_H}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k}.
\label{eq:befapprox}
\end{equation}
In the notation $Y_{\Lambda}$, index $\Lambda$ refers to the size of set $\mathcal{A}$ (this notation will be helpful later in this section). For our theoretical analysis we assume that $X$'s are identically distributed such that $X_{i_1,i_2,\dots,i_H}\sim\mathcal{N}(0,1)$.

@@

Consider $(s,\epsilon)$-reduction image of $\mathcal{N}$ for some $s \leq \Lambda$ and $\epsilon \in [0,1]$. The output $Y_s$ of the image network can in general be expressed as
\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}\!\!w_{i_k},
\]
where $r_{i_1,\dots,i_H}^{'} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ repeats in Equation~\ref{eq:befapprox} and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{'} = \Psi$. We can further rewrite $Y_s$ as follows
\[Y_s = q\!\!\!\sum_{i_1,\dots,i_H=1}^{s}\!\!\underbrace{\left(\!\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}\!\!\!X_{i_1,\dots,i_H} + 0 + \dots + 0\right)}_{r_{i_1,\dots,i_H}^{''} \text{summands}}\!\!\rho\prod_{k = 1}^{H}\!\!w_{i_k},
\]
where $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$ is the number of times each configuration $(w_{i_1},w_{i_2},\dots,w_{i_H})$ would repeat in Equation~\ref{eq:befapprox} if all $r_{i_1,\dots,i_H}$ would be equal to $1$ and $\mathcal{W}$ would have $s$ unique weights and the remaining $(\Lambda - s)$ weights were repetitions\footnote{Note that each $r_{i_1,\dots,i_H}^{''}$ is not uniquely defined here as one could consider many different ways of constructing $\mathcal{W}$ by repeating the same weights different times.}. We therefore require that $r_{i_1,\dots,i_H}^{''} \in \{\mathbb{Z}^{+}\cup{0}\}$, $r_{i_1,\dots,i_H}^{''} \geq r_{i_1,\dots,i_H}^{'}$ and $\sum_{i_1,\dots,i_H=1}^{s}r_{i_1,\dots,i_H}^{''} = \Lambda^H$. We furthermore define $Z$'s to be independend standard normal random variables satisfying the following (plethora of similar decoupling strategies are discussed in~\cite{opac-b1095246})
\[\sum_{j=1}^{r_{i_1,\dots,i_H}^{'}}X_{i_1,\dots,i_H} = \sum_{j=1}^{r_{i_1,\dots,i_H}^{''}} \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}Z_{i_1,\dots,i_H}^{(j)}. 
\]
Let $\hat{r}_{i_1,\dots,i_H}^{(j)} = \sqrt{\frac{r_{i_1,\dots,i_H}^{'}}{r_{i_1,\dots,i_H}^{''}}}$. Therefore
\begin{eqnarray*}
Y_s &=& q\sum_{i_1,\dots,i_H=1}^{s}\sum_{j=1}^{r_{i_1,\dots,i_H}^{''}}\hat{r}_{i_1,\dots,i_H}^{(j)}Z_{i_1,\dots,i_H}^{(j)}\rho\prod_{k = 1}^{H}w_{i_k}\\
&=& \sum_{i_1,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,\dots,i_H}Z_{i_1,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
\end{eqnarray*}
where the last step comes from re-indexing terms.

Finally we assume that unique weights are close to being evenly distributed on the graph of connections of network $\mathcal{M}$. We call this assumption a \textit{uniformity assumption} (note it is analogous to the maximum entropy assumption). This assumption is in general consistent with the approach in~\cite{NIPS2013_5025}. To be more specific, this assumption implies that for all $(i_1,i_2,\dots,i_H):i_1,i_2,\dots,i_H \in \{1,2,\dots,H\}$ there exists non-negative constant $c$ and $\delta \in [0,1]$ such that the following holds
\begin{equation}
c\delta\sqrt{\frac{\Psi}{\Lambda^H}} \leq \hat{r}_{i_1,i_2,\dots,i_H} \leq c\sqrt{\frac{\Psi}{\Lambda^H}},
\label{eq:uniform}
\end{equation}
where the factor $\sqrt{\frac{\Psi}{\Lambda^H}}$ comes from the fact that for the network where every weight is uniformly distributed on the graph of connections (thus every node has equal probability of being adjacent to an edge with any of the unique weights) it holds that $\hat{r}_{i_1,i_2,\dots,i_H} = \sqrt{\frac{\Psi}{\Lambda^H}}$. Note that this condition can be sattified with large $\delta$ (close to $0$) if $s$ is sufficiently small.

Consider therefore an expression as follows
\begin{equation}
\hat{Y}_s = q\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}Z_{i_1,i_2,\dots,i_H}\rho\prod_{k = 1}^{H}w_{i_k},
\label{eq:approx}
\end{equation}
which can be thought of as an output of some network $\mathcal{M}$ where the weights are still chosen from $\mathcal{A}$ but there are only $s$ unique weights in $\mathcal{A}$ among the total of $\Lambda$ weights, and furthermore every $H$ - length configuration of weights chosen from $\mathcal{A}$ is equally likely. Then the following theorem (Theorem~\ref{thm:unif}) captures the connection between $\hat{Y}_s$ and $Y_{\Lambda}$.

\begin{theorem}
Under the uniformity assumption of Equation~\ref{eq:uniform}, random variable $\hat{Y}_s$ in Equation~\ref{eq:approx} and random variable $Y_{\Lambda}$ in Equation~\ref{eq:befapprox} sattisy the following
\[corr(\hat{Y}_s,Y_{\Lambda}) \geq \delta
\]
\label{thm:unif}
\end{theorem}

We will refer to $\hat{Y}_s$ as an $(s,\epsilon,\delta)$-\textit{approximator} of $Y_{\Lambda}$, where the quality of this approximation is captured in Theorems~\ref{thm:redun} and~\ref{thm:unif}. Intuitively, for large-size networks (our analysis in Section~\ref{sec:theory} considers $\Lambda \rightarrow \infty$) one would expect $s$ to be small enough to simultaneously guarantee sufficiently large (close to $1$) $\delta$ and preserve good accuracy (small $\epsilon$). \textcolor{red}{That is because large networks have significantly more modelling power thus small $s$ is a natural form of controlling the overfitting. Besides then the data is mapped to a higher dimensional space.} Next we will consider two frequently used loss functions, absolute loss and hinge loss, where we approximate $Y_{\Lambda}$ with $\hat{Y}_s$.

@@

\section{Proof of Theorem~\ref{thm:redun}}
\begin{proof}
Note that $\mathbb{E}[\hat{Y}_s] = 0$ and $\mathbb{E}[Y_{\Lambda}] = 0$. Furthermore
\[\mathbb{E}[\hat{Y}_sY_{\Lambda}] = q^2\rho^2\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}\hat{r}_{i_1,i_2,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2
\]
and
\[std(\hat{Y}_s) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2}
\]
\[std(Y_{\Lambda}) = q\rho\sqrt{\sum_{i_1,i_2,\dots,i_H=1}^{\Lambda}\hat{r}_{i_1,i_2,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2}.
\]
Therefore
\begin{eqnarray*}
&&\!\!\!\!\!\!\!\!\!corr(\hat{Y}_s,Y_{\Lambda})\\ 
&\!\!\!\!\!\!\!\!\!=&\!\!\!\!\!\!\! \frac{\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\sqrt{\frac{\Psi}{\Lambda^H}}\hat{r}_{i_1,\dots,i_H}\prod_{k = 1}^{H}w_{i_k}^2}{\sqrt{\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\frac{\Psi}{\Lambda^H}\prod_{k = 1}^{H}w_{i_k}^2\right)\!\!\!\!\left(\displaystyle\sum_{i_1,\dots,i_H=1}^{\Lambda}\!\!\!\!\!\hat{r}_{i_1,\dots,i_H}^2\prod_{k = 1}^{H}w_{i_k}^2\right)}}\\
&\!\!\!\!\!\!\!\!\geq& \delta, 
\end{eqnarray*}
where the last inequality is the direct consequence of the uniformity assumption of Equation~\ref{eq:uniform}.
\end{proof}
